### 2017-09-29 TF-vldb2018/sec-intro.tex

A headhunt helps to set up a team for developing a software product by searching proper candidates from $G_1$ (ignore dashed edges).
A desired team has
(a) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
(b) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.

@@

One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,realTeamForm13}, can hardly find a desired team.
They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (a)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (b)).
 \end{example}

@@

\stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching .
We also propose two optimization techniques, incrementally computing radius varied balls and density based filtering, for speeding up computations.

>>>>

A headhunt helps to set up a team for developing a software product by searching proper candidates from $G_1$ (ignore dashed edges).
A desired team has
(i) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
(ii) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.

@@

One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,realTeamForm13}, can hardly find a desired team.
They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (i)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (ii)).
 \end{example}

@@

\stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching.
We also propose two optimization techniques, incrementally computing radius varied balls and density based filtering, for speeding up computations.

### 2017-09-29 TF-vldb2018/sec-tsim.tex

%\vspace{-4ex}
\subsection{Pattern Matching for Team Formation}
\label{subsec-extsim}

@@

\begin{example}
\label{exa-teamF}
Consider $P_1, G_1$ in Fig.~\ref{exm-motivation} and $r=2$.
We simply set $k=1$, as most existing solutions for \teamF{} only compute the best team \cite{Lappas09,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12}, instead of top-$k$ teams.

@@

One may already notice that these teams only satisfy the skill requirement, \ie condition (a) in Example \ref{exm-motivation}, and cannot guarantee  the specific collaboration relationships among team members.
Indeed, the team found in (1) and (2) is connected by \kw{BA_3} only, and the team found in (3) has loose collaborations among its members.
That is, existing methods are not appropriate for identifying the the desired teams.

When team simulation is adopted, it returns the perfect subgraph in Example \ref{exm-rsimulation} with its density = 1.4,
satisfying both conditions (a) and (b), much better than those teams found by the above existing methods.
\end{example}

@@

\stitle{Pattern updates}. There are five types of pattern updates:
%
(1) {\em edge insertions} connecting nodes in $P$,
%
(2) {\em edge deletions} disconnecting nodes in $P$,
%
(3) {\em node insertions} attaching new nodes to $P$,
%
(4) {\em node deletions} removing nodes from $P$, and
%
(5) {\em capacity changes} adjusting the node capacities in $P$,
%
while $P$  remains connected in all cases.

\stitle{Data updates}. There are four types of data updates, which can be
defined along the same lines as the first four types of pattern updates.
Further, different from pattern updates, there is no need to keep $G$ connected for data updates.

>>>>

%\vspace{-4ex}
\subsection{Team Formation}
\label{subsec-extsim}

@@

\begin{example}
\label{exa-teamF}
Consider $P_1, G_1$ in Fig.~\ref{exm-motivation} and $r=2$.
We simply set $k=1$, as most existing solutions for \teamF{} only compute the best team \cite{Lappas09,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12}.

@@

One may already notice that these teams only satisfy the skill requirement, \ie condition (i) in Example \ref{exm-motivation}, and cannot guarantee  the specific collaboration relationships among team members.
Indeed, the team found in (1) and (2) is connected by \kw{BA_3} only, and the team found in (3) has loose collaborations among its members.
That is, existing methods are not appropriate for identifying the the desired teams.

When team simulation is adopted, it returns the perfect subgraph in Example \ref{exm-rsimulation} with its density = 1.4,
satisfying both conditions (i) and (ii), much better than those teams found by the above existing methods.
\end{example}

@@

\stitle{Pattern updates ($\Delta P$)}. There are five types of pattern updates:
%
(1) {\em edge insertions} connecting nodes in $P$,
%
(2) {\em edge deletions} disconnecting nodes in $P$,
%
(3) {\em node insertions} attaching new nodes to $P$,
%
(4) {\em node deletions} removing nodes from $P$, and
%
(5) {\em capacity changes} adjusting the node capacities in $P$,
%
while $P$  remains connected in all cases.

\stitle{Data updates ($\Delta G$)}. There are four types of data updates,
defined along the same lines as the first four types of pattern updates.
Further, different from pattern updates, there is no need to keep $G$ connected for data updates.
